Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-19 Draft.Rmd
scaled train for knn

# Check performance of linear regression model on the complete training data
res1 %>% 
    extract_fit_engine() %>% 
    summary()

@@

```{r kNN}
# Find ideal k clusters

# Scale the training data for k-NN model
train_scales
origin_scaled <- origin %>% 
    mutate(across(-value, scale))

# Create kNN model
model2 <- nearest_neighbor(neighbors = 5) %>% 
    set_engine("kknn") %>% 
    set_mode("regression")

@@

# Fit the model on the full training dataset using the `fit()` function
res2 <- fit(wf2, data = train)

@@

# Check performance using cross-validation
folds <- vfold_cv(train, v = 10)
folds
res2 <- fit_resamples(wf2, resamples = folds) #error Assigned data `orig_rows` must be compatible with existing data.
res2 %>% 
    collect_metrics()
```

>>>>

# Check performance of linear regression model on the training data
res1 %>% 
    extract_fit_engine() %>% 
    summary()

@@

```{r kNN}
# Find ideal k neighbors
sqrt(nrow(train))

# Scale the training data for k-NN model
train_scaled = train |> dplyr::select(where(is.numeric)) |> mutate(across(fips:aod, scale)) |> cbind(state=train$state,county=train$county,city=train$city)

# Create kNN model
model2 <- nearest_neighbor(neighbors = 26) %>% 
    set_engine("kknn") %>% 
    set_mode("regression")

@@

# Fit the model on the full training dataset using the `fit()` function
res2 <- fit(wf2, data = train_scaled)

@@

# Check performance using cross-validation
folds <- vfold_cv(train, v = 10)
folds
res2 <- fit_resamples(wf2, resamples = folds) # error Assigned data `orig_rows` must be compatible with existing data.
res2 %>% 
    collect_metrics()
```
